Different rules for binocular combination of luminance flicker in cortical and subcortical pathways

### 2023-08-28 manuscript.Rmd
Updater authors' inofrmation

---
title: "Different rules for binocular combination of luminance flicker in cortical and subcortical pathways"
author: |
 | Federico G. Segala, Aurelio Bruno, Joel T. Martin, 
 | Myat T. Aung, Alex R. Wade & Daniel H. Baker
 | Department of Psychology, University of York, UK
 | *eLife* (2023) https://doi.org/10.7554/eLife.87048
output:
  bookdown::pdf_document2:
    fig_caption: yes
    toc: no
    keep_tex: yes
  word_document2: default
  html_document: default
bibliography: references.bib
link-citations: true
csl: elife.csl
header-includes:
- \usepackage{float}
- \usepackage{float} \floatplacement{figure}{H}
- \newcommand{\beginsupplement}{\setcounter{table}{0}
- \renewcommand{\thetable}{A\arabic{table}}
- \setcounter{figure}{0}
- \renewcommand{\thefigure}{A\arabic{figure}}}
- \usepackage{caption}
---

@@

>>>>

---
title: "Different rules for binocular combination of luminance flicker in cortical and subcortical pathways"
author: |
 | Federico G. Segala$^1$, Aurelio Bruno$^2$, Joel T. Martin$^1$, Myat T. Aung$^1$, Alex R. Wade$^1$
 | & Daniel H. Baker$^1$
 | *eLife* (2023) https://doi.org/10.7554/eLife.87048
output:
  bookdown::pdf_document2:
    fig_caption: yes
    toc: no
    keep_tex: yes
  word_document2: default
  html_document: default
bibliography: references.bib
link-citations: true
csl: elife.csl
header-includes:
- \usepackage{float}
- \usepackage{float} \floatplacement{figure}{H}
- \newcommand{\beginsupplement}{\setcounter{table}{0}
- \renewcommand{\thetable}{A\arabic{table}}
- \setcounter{figure}{0}
- \renewcommand{\thefigure}{A\arabic{figure}}}
- \usepackage{caption}
---

@@

$^1$Department of Psychology, University of York, York, UK. YO10 5DD  
$^2$School of Psychology and Vision Sciences, University of Leicester, Leicester, UK. LE1 7RH

Address for correspondence: Federico G. Segala, [fgs502\@york.ac.uk](fgs502@york.ac.uk)
